#Pre-treatment measures and experimental vignette

```{r 1031_packages, include=FALSE}
if(!require("broom")){install.packages("broom");  library(broom)}
if(!require("devtools")){install.packages("devtools");  library(devtools)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
options(kableExtra.latex.load_packages = FALSE) 
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("naniar")){install.packages("naniar");  library(naniar)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}

set.seed(2016)
## Utils. 
source("goodloser-utils.R")

d <- read_sav("Data/Goodloser-exp1.sav")

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", warning = FALSE, message = FALSE)

```

##Pre-treatment measures
```{r 1031_main}

d %>% group_by(opinion_ban) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100),
         opinion_ban = case_when(opinion_ban == 'Anti' ~ 'Against ban',
                                 opinion_ban == 'Pro' ~ 'For ban')) %>%
  ungroup() %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on a ban on begging in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-begging-pref-swevig.html"))

d %>% mutate(
     opinion_strength = case_when(
      opinion_strength == 1 ~ "1 Not important at all",
      opinion_strength == 2 ~ "2",
      opinion_strength == 3 ~ "3",
      opinion_strength == 4 ~ "4",
      opinion_strength == 5 ~ "5",
      opinion_strength == 6 ~ "6",
      opinion_strength == 7 ~ "7 Very important")) %>% 
  group_by(opinion_strength) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%
  ungroup() %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of ban on begging to you personally?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-begging-importance-swevig.html"))
```

##Experimental vignette

*Experimental vignette.*

>Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders. The decision can be made in different ways: One option is that the local political representatives make the decision. Another option is that the citizens of the municipality decide through a referendum. Please image how you would react if this scenario occurred in your municipality: After a debate in the media, the local political representatives decide to ban begging in the municipality. *Treatment text follows.*

```{r 1031_vignette}
table <- tibble(Treatment = c("No prime", "Lamenting politician", "General prime"), Text = c("Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders. The decision can be made in different ways: One option is that the local political representatives make the decision. Another option is that the citizens of the municipality decide through a referendum. Please image how you would react if this scenario occurred in your municipality: After a debate in the media, the local political representatives decide to ban begging in the municipality.", 
                                                                                             "Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders. The decision can be made in different ways: One option is that the local political representatives make the decision. Another option is that the citizens of the municipality decide through a referendum. Please image how you would react if this scenario occurred in your municipality: After a debate in the media, the local political representatives decide to ban begging in the municipality. After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong.",
                                                                                             "Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders. The decision can be made in different ways: One option is that the local political representatives make the decision. Another option is that the citizens of the municipality decide through a referendum. Please image how you would react if this scenario occurred in your municipality: After a debate in the media, the local political representatives decide to ban begging in the municipality. After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong, but that's how it is like living in a democracy.")
                )%>% 
    mutate_all(linebreak) %>% 
    kable(booktabs = T, linesep = "", escape = F,  caption = "Vignette treatments and texts, Swedish vignette experiment", col.names = linebreak(c("Treatment", "Text"))) %>% 
    collapse_rows(columns = 1, latex_hline = "major", valign = "top") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))%>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-vignette-swevig.html"))

```

```{r 1031_outcome_measures}

d %>% mutate(
  fairness = case_when(
      fairness == 1 ~ "1 Not fair at all",
      fairness == 2 ~ "2",
      fairness == 3 ~ "3",
      fairness == 4 ~ "4",
      fairness == 5 ~ "5",
      fairness == 6 ~ "6",
      fairness == 7 ~ "7 Very fair")) %>% 
  group_by(fairness) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent")))%>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-dv-fairness-swevig.html"))

d %>% mutate(
   justice = case_when(
      justice == 1 ~ "1 Not just at all",
      justice == 2 ~ "2",
      justice == 3 ~ "3",
      justice == 4 ~ "4",
      justice == 5 ~ "5",
      justice == 6 ~ "6",
      justice == 7 ~ "7 Very just")) %>% 
  group_by(justice) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "How just do you think the decision procedure was?", col.names = linebreak(c("Value", "N", "Percent")))%>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-dv-justice-swevig.html"))

d %>% mutate(
     eval = case_when(
      eval == 1 ~ "1 Very bad",
      eval == 2 ~ "2",
      eval == 3 ~ "3",
      eval == 4 ~ "4",
      eval == 5 ~ "5",
      eval == 6 ~ "6",
      eval == 7 ~ "7 Very good")) %>% 
  group_by(eval) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "What do you think in general about the decision?", col.names = linebreak(c("Value", "N", "Percent")))%>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-dv-evaluation-swevig.html"))

d %>% mutate(
  comply = case_when(
      comply == 1 ~ "1 Not willing at all",
      comply == 2 ~ "2",
      comply == 3 ~ "3",
      comply == 4 ~ "4",
      comply == 5 ~ "5",
      comply == 6 ~ "6",
      comply == 7 ~ "7 Very willing")) %>% 
  group_by(comply) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "How willing are you to accept and comply with the decision?", col.names = linebreak(c("Value", "N", "Percent")))%>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-dv-accept-swevig.html"))

```

