# Pre-treatment measures and experimental vignette
The statistics are displayed for the respondents of interest in this study, which is the respondents who end up with observing an unfavorable decision outcome in the experiment.

```{r 1031_packages, include=FALSE}
if(!require("broom")){install.packages("broom");  library(broom)}
if(!require("devtools")){install.packages("devtools");  library(devtools)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
options(kableExtra.latex.load_packages = FALSE) 
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("naniar")){install.packages("naniar");  library(naniar)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}

set.seed(2016)
## Utils. 
source("goodloser-utils.R")

d <- read_sav("Data/Goodloser-exp1.sav")
#Filter on respondents who receive an unfavorable outcome
d <- d %>% 
  filter(favorability == "Unfavorable") 

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", warning = FALSE, message = FALSE)

```

## Pre-treatment measures

### Ban on begging - opinion
```{r 1031_pre_begging}
#for bookdown
d %>% group_by(opinion_ban) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100),
         opinion_ban = case_when(opinion_ban == 'Anti' ~ 'Against ban',
                                 opinion_ban == 'Pro' ~ 'For ban')) %>%
  ungroup() %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on a ban on begging in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")

#save to file
d %>% group_by(opinion_ban) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100),
         opinion_ban = case_when(opinion_ban == 'Anti' ~ 'Against ban',
                                 opinion_ban == 'Pro' ~ 'For ban')) %>%
  ungroup() %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on a ban on begging in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-begging-pref-swevig.html"))
```

### Ban on begging - importance
```{r 1031_pre_begging2}
#for bookdown
d %>% mutate(
     opinion_strength = case_when(
      opinion_strength == 1 ~ "1 Not important at all",
      opinion_strength == 2 ~ "2",
      opinion_strength == 3 ~ "3",
      opinion_strength == 4 ~ "4",
      opinion_strength == 5 ~ "5",
      opinion_strength == 6 ~ "6",
      opinion_strength == 7 ~ "7 Very important")) %>% 
  group_by(opinion_strength) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%
    ungroup() %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of ban on begging to you personally?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  footnote(footnote_as_chunk = ) %>% 
  kable_styling(latex_options = "HOLD_position")

#save to file
d %>% mutate(
     opinion_strength = case_when(
      opinion_strength == 1 ~ "1 Not important at all",
      opinion_strength == 2 ~ "2",
      opinion_strength == 3 ~ "3",
      opinion_strength == 4 ~ "4",
      opinion_strength == 5 ~ "5",
      opinion_strength == 6 ~ "6",
      opinion_strength == 7 ~ "7 Very important")) %>% 
  group_by(opinion_strength) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%
  ungroup() %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of ban on begging to you personally?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-begging-importance-swevig.html"))
```
The mean score for the pre treatment measure "How important is the issue of ban on begging to you personally?" is `r round(mean(d$opinion_strength), digits=2)`, and the standard deviation is `r round(sd(d$opinion_strength), digits=2)`.

## Experimental vignette

*Experimental vignette.*

>Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders. The decision can be made in different ways: One option is that the local political representatives make the decision. Another option is that the citizens of the municipality decide through a referendum. Please image how you would react if this scenario occurred in your municipality: After a debate in the media, the local political representatives decide to ban begging in the municipality. *Treatment text follows.*

```{r 1031_vignette}
table <- tibble(Treatment = c("No prime", "Lamenting politician", "Generic good loser prime"), Text = c("Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders. The decision can be made in different ways: One option is that the local political representatives make the decision. Another option is that the citizens of the municipality decide through a referendum. Please image how you would react if this scenario occurred in your municipality: After a debate in the media, the local political representatives decide to ban begging in the municipality.", 
                                                                                             "Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders. The decision can be made in different ways: One option is that the local political representatives make the decision. Another option is that the citizens of the municipality decide through a referendum. Please image how you would react if this scenario occurred in your municipality: After a debate in the media, the local political representatives decide to ban begging in the municipality. After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong.",
                                                                                             "Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders. The decision can be made in different ways: One option is that the local political representatives make the decision. Another option is that the citizens of the municipality decide through a referendum. Please image how you would react if this scenario occurred in your municipality: After a debate in the media, the local political representatives decide to ban begging in the municipality. After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong, but that's how it is like living in a democracy.")
                )%>% 
    mutate_all(linebreak)

#for bookdown
kable(table, booktabs = T, linesep = "", escape = F,  caption = "Vignette treatments and texts, Swedish vignette experiment", col.names = linebreak(c("Treatment", "Text"))) %>% 
    collapse_rows(columns = 1, latex_hline = "major", valign = "top") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
#save to file
kable(table, booktabs = T, linesep = "", escape = F,  caption = "Vignette treatments and texts, Swedish vignette experiment", col.names = linebreak(c("Treatment", "Text"))) %>% 
    collapse_rows(columns = 1, latex_hline = "major", valign = "top") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))%>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-vignette-swevig.html"))

```

## Post treatment measures
### Fairness
```{r 1031_outcome_measures_fairness}

d %>% mutate(
  fairness = case_when(
      fairness == 1 ~ "1 Not fair at all",
      fairness == 2 ~ "2",
      fairness == 3 ~ "3",
      fairness == 4 ~ "4",
      fairness == 5 ~ "5",
      fairness == 6 ~ "6",
      fairness == 7 ~ "7 Very fair")) %>% 
  group_by(fairness) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent")))%>% 
  kable_styling(latex_options = "HOLD_position")


d %>% mutate(
  fairness = case_when(
      fairness == 1 ~ "1 Not fair at all",
      fairness == 2 ~ "2",
      fairness == 3 ~ "3",
      fairness == 4 ~ "4",
      fairness == 5 ~ "5",
      fairness == 6 ~ "6",
      fairness == 7 ~ "7 Very fair")) %>% 
  group_by(fairness) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>% 
  kable(booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent")))%>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "swevig", "tbls", "html", "tbl-dv-fairness-swevig.html"))

```
The mean score for the post treatment measure "What do you think about the way the decision was made?" is `r round(mean(d$fairness), digits=2)`, and the standard deviation is `r round(sd(d$fairness), digits=2)`.

<!-- ### Justice -->
<!-- ```{r 1031_outcome_measure_justice} -->

<!-- d %>% mutate( -->
<!--    justice = case_when( -->
<!--       justice == 1 ~ "1 Not just at all", -->
<!--       justice == 2 ~ "2", -->
<!--       justice == 3 ~ "3", -->
<!--       justice == 4 ~ "4", -->
<!--       justice == 5 ~ "5", -->
<!--       justice == 6 ~ "6", -->
<!--       justice == 7 ~ "7 Very just")) %>%  -->
<!--   group_by(justice) %>% -->
<!--    summarize(N_obs = n()) %>%  -->
<!--   mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%  -->
<!--   kable(booktabs = TRUE, linesep = "", escape = F, caption = "How just do you think the decision procedure was?", col.names = linebreak(c("Value", "N", "Percent")))%>%  -->
<!--   kable_styling(latex_options = "HOLD_position") -->

<!-- d %>% mutate( -->
<!--    justice = case_when( -->
<!--       justice == 1 ~ "1 Not just at all", -->
<!--       justice == 2 ~ "2", -->
<!--       justice == 3 ~ "3", -->
<!--       justice == 4 ~ "4", -->
<!--       justice == 5 ~ "5", -->
<!--       justice == 6 ~ "6", -->
<!--       justice == 7 ~ "7 Very just")) %>%  -->
<!--   group_by(justice) %>% -->
<!--    summarize(N_obs = n()) %>%  -->
<!--   mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%  -->
<!--   kable(booktabs = TRUE, linesep = "", escape = F, caption = "How just do you think the decision procedure was?", col.names = linebreak(c("Value", "N", "Percent")))%>%  -->
<!--   kable_styling(latex_options = "HOLD_position") %>%  -->
<!--   cat(., file = here("output", "swevig", "tbls", "html", "tbl-dv-justice-swevig.html")) -->
<!-- ``` -->
<!-- The mean score for the post treatment measure "How just do you think the decision procedure was?" is `r round(mean(d$justice), digits=2)`, and the standard deviation is `r round(sd(d$justice), digits=2)`. -->

<!-- ### Evaluation -->
<!-- ```{r 1031_outcome_measure_eval} -->
<!-- d %>% mutate( -->
<!--      eval = case_when( -->
<!--       eval == 1 ~ "1 Very bad", -->
<!--       eval == 2 ~ "2", -->
<!--       eval == 3 ~ "3", -->
<!--       eval == 4 ~ "4", -->
<!--       eval == 5 ~ "5", -->
<!--       eval == 6 ~ "6", -->
<!--       eval == 7 ~ "7 Very good")) %>%  -->
<!--   group_by(eval) %>% -->
<!--    summarize(N_obs = n()) %>%  -->
<!--   mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%  -->
<!--   kable(booktabs = TRUE, linesep = "", escape = F, caption = "What do you think in general about the decision?", col.names = linebreak(c("Value", "N", "Percent")))%>%  -->
<!--   kable_styling(latex_options = "HOLD_position")  -->

<!-- d %>% mutate( -->
<!--      eval = case_when( -->
<!--       eval == 1 ~ "1 Very bad", -->
<!--       eval == 2 ~ "2", -->
<!--       eval == 3 ~ "3", -->
<!--       eval == 4 ~ "4", -->
<!--       eval == 5 ~ "5", -->
<!--       eval == 6 ~ "6", -->
<!--       eval == 7 ~ "7 Very good")) %>%  -->
<!--   group_by(eval) %>% -->
<!--    summarize(N_obs = n()) %>%  -->
<!--   mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%  -->
<!--   kable(booktabs = TRUE, linesep = "", escape = F, caption = "What do you think in general about the decision?", col.names = linebreak(c("Value", "N", "Percent")))%>%  -->
<!--   kable_styling(latex_options = "HOLD_position") %>%  -->
<!--   cat(., file = here("output", "swevig", "tbls", "html", "tbl-dv-evaluation-swevig.html")) -->
<!-- ``` -->
<!-- The mean score for the post treatment measure "What do you think in general about the decision?" is `r round(mean(d$eval), digits=2)`, and the standard deviation is `r round(sd(d$eval), digits=2)`. -->

<!-- ### Acceptance -->
<!-- ```{r 1031_outcome_measure_comply} -->
<!-- d %>% mutate( -->
<!--   comply = case_when( -->
<!--       comply == 1 ~ "1 Not willing at all", -->
<!--       comply == 2 ~ "2", -->
<!--       comply == 3 ~ "3", -->
<!--       comply == 4 ~ "4", -->
<!--       comply == 5 ~ "5", -->
<!--       comply == 6 ~ "6", -->
<!--       comply == 7 ~ "7 Very willing")) %>%  -->
<!--   group_by(comply) %>% -->
<!--    summarize(N_obs = n()) %>%  -->
<!--   mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%  -->
<!--   kable(booktabs = TRUE, linesep = "", escape = F, caption = "How willing are you to accept and comply with the decision?", col.names = linebreak(c("Value", "N", "Percent")))%>%  -->
<!--   kable_styling(latex_options = "HOLD_position") -->

<!-- t <- d %>% mutate( -->
<!--   comply = case_when( -->
<!--       comply == 1 ~ "1 Not willing at all", -->
<!--       comply == 2 ~ "2", -->
<!--       comply == 3 ~ "3", -->
<!--       comply == 4 ~ "4", -->
<!--       comply == 5 ~ "5", -->
<!--       comply == 6 ~ "6", -->
<!--       comply == 7 ~ "7 Very willing")) %>%  -->
<!--   group_by(comply) %>% -->
<!--    summarize(N_obs = n()) %>%  -->
<!--   mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%  -->
<!--     kable(booktabs = TRUE, linesep = "", escape = F, caption = "How willing are you to accept and comply with the decision?", col.names = linebreak(c("Value", "N", "Percent")))%>%  -->
<!--   kable_styling(latex_options = "HOLD_position") %>%  -->
<!--   cat(., file = here("output", "swevig", "tbls", "html", "tbl-dv-accept-swevig.html")) -->
<!-- ``` -->
<!-- The mean score for the post treatment measure "How willing are you to accept and comply with the decision?" is `r round(mean(d$comply), digits=2)`, and the standard deviation is `r round(sd(d$comply), digits=2)`. -->

