```{r setup, include=FALSE}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("utf8")){install.packages("utf8");  library(utf8)}

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", warning = FALSE, message = FALSE)
```

#Stimulus material

Video voice over text: "Imagine that your municipality is about to decide whether begging on the streets should be banned or allowed within the municipal borders in the future. This is a controversial decision: Some inhabitants and politicians strongly support the ban, while other inhabitants and politicians are equally strongly against such a ban on begging. Some parties propose a ban on begging. The decision will be made in the municipal council, and follows the normal decision-making procedure. The proposal is  rst debated in the council, where all members are welcome to express their position and their arguments. The debate is public, and journalists are present to report on the debate. In the end, the politicians vote on the proposal." 

```{r}
table <- tibble(Preference = c("Pro ban on begging", "Pro ban\non begging", "Pro ban\non begging", "Pro ban\non begging", "Pro ban\non begging", "Against ban on begging", "Against ban\non begging", "Against ban\non begging", "Against ban\non begging", "Against ban\non begging"), 
                Treatment = c("No prime", "Lamenting politician", "General prime", "Specific prime", "Winner", "No prime", "Lamenting politician", "General prime", "Specific prime", "Winner"), 
                Text = c("The majority votes against a ban on begging. That means the council will not ban begging in your municipality.",
                         "The majority votes against a ban on begging. That means the council will not ban begging in your municipality.After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong.",
                         "The majority votes against a ban on begging. That means the council will not ban begging in your municipality. After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong, \nbut that's how it is like living in a democracy. Sometimes you win, sometimes you lose.",
                         "The majority votes against a ban on begging. That means the council will not ban begging in your municipality. After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong, \nbut that it was a fair fight where both sides had the chance to defend their positions.",
                         "The majority votes for a ban on begging. That means the council will ban begging in your municipality.",
                         "The majority votes for a ban on begging. That means the council will ban begging in your municipality.", 
                         "The majority votes for a ban on begging. That means the council will ban begging in your municipality. After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong.", 
                         "The majority votes for a ban on begging. That means the council will ban begging in your municipality. After the decision, the leader of one of the parties who where in favor of a ban states that they are disappointed and that the decision was wrong, \nbut that's how it is like living in a democracy. Sometimes you win, sometimes you lose.",
                         "The majority votes for a ban on begging. That means the council will ban begging in your municipality. After the decision, the leader of one of the partieswho where in favor of a ban states that they are disappointed and that the decision was wrong, \nbut that it was a fair fight where both sides had the chance to defend their positions.",
                         "The majority votes against a ban on begging. That means the council will not ban begging in your municipality.")
)


  table %>% 
    mutate_all(linebreak) %>% 
    kable(booktabs = T, linesep = "", escape = F,  caption = "Vignette text per treatment", col.names = linebreak(c("Preference", "Treatment", "Text"))) %>% 
    collapse_rows(columns = 1, latex_hline = "major", valign = "top") %>% 
  kable_styling(latex_options = c("striped", "scale_down")) %>% 
  cat(., file = here("output", "novig", "tbls", "html",  "tbl-vignette-novig.html"))

```