# Main effects with sample that excludes respondents who fail manipulation check

> This chapter explores the first hypothesis in the [pre-registration](GoogLoser_Prereg_3_#16823[16065].pdf) of the experiment: **Individuals that receive an unfavorable outcome express lower fairness perception than individuals that receive a favorable outcome.** The estimation of the Average Marginal Component Effects is based on the function developed by Mikael P. Johannesson, and available on [Github](https://rdrr.io/github/mikajoh/descr2/man/amce.html). 

```{r 2045_packages, include=FALSE}
if(!require("broom")){install.packages("broom");  library(broom)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
options(kableExtra.latex.load_packages = FALSE) 
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("naniar")){install.packages("naniar");  library(naniar)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
# The analysis uses custom functions included in the compendium. Install the included pkg with `devtools::install()` or just install from github with:
#if (!require(wiggle)) {  devtools::install_github("mikajoh/wiggle")}

set.seed(2016)
## Utils. 
source("goodloser-utils.R")

d <- read_sav("Data/Goodloser-exp2-exclusive.sav")

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", warning = FALSE, message = FALSE)
```

##Prepare data
```{r 2045_main}

d <- d %>%
  mutate(treatment = lvls_reorder(treatment, c(3, 2, 1, 4, 5)) 
  )
``` 

##Fairness
```{r 2045_post_fairness}

res_main <-  lm(fairness ~ treatment, data = d) 
res_main <- broom::tidy(res_main)

labels <- data.frame(
  term = c(
    "treatmentLamenting politician",
    "treatmentGeneral Prime",
    "treatmentSpecific prime",
    "treatmentWinner"
    
  ),
  label = c( "Lamenting politician",
             "General prime",
             "Specific prime",
             "Winner")
)
#Figure
fig <-   res_main %>%
  filter(term != "(Intercept)") %>% 
  left_join(labels, by = "term") %>% 
  
  ggplot(aes(x = estimate, y = label,
             xmin = estimate - (2 * std.error),
             xmax = estimate + (2 * std.error))) +
   geom_errorbarh(height = 0) +
  geom_point() +
  geom_vline(aes(xintercept = 0), linetype = "dotted") +
  scale_x_continuous(limits = c(-1, 1),
                     breaks = round(seq(-1, 1, .25), 2),
                     expand = c(0, 0)) +
  ggtitle('Treatment effects on fairness perceptions of decision, Study 2 -- Norwegian vignette. Sample: Respondents who pass manipulation check') +
  labs(x = "Change in fairness perception",
       y = "Decision process attributes") +
  theme_bw() +
  theme(plot.margin = unit(c(2, 2, 2, 2), "mm"), axis.text.x=element_text(size=rel(0.7))) +
  theme(panel.spacing = unit(0.5, "lines"))
fig

ggsave(
  here("output", "novig", "figs", "pngs", "exp2-fairness-mainfig-mcheck.png"),
  plot = fig,
  width = 5.5, height = 2.75
)

ggsave(
  here("output", "novig", "figs", "pdfs", "exp2-fairness-mainfig-mcheck.pdf"),
  plot = fig,
  width = 5.5, height = 2.75
)


#Table
table <- res_main %>% 
  select(term, estimate, std.error, statistic, p.value) %>% 
  mutate(term = case_when( term == "(Intercept)" ~ "Not shown",
                    term == "treatmentLamenting politician" ~ "Lamenting politician",
                   term == "treatmentGeneral Prime" ~ "General prime", 
                   term == "treatmentSpecific prime" ~ "Specific prime",
                   term == "treatmentWinner" ~ "Winner"))

kable(table, booktabs = TRUE, caption = "Treatment effects on fairness perceptions of decision, Study 2 -- Norwegian vignette. Sample: Respondents who pass manipulation check", col.names = linebreak(c("Treatment value", "Estimate", "Std. Error", "t-statistic", "p value")), digits = 2) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>% 
  cat(., file = here("output", "novig", "tbls", "html",  "tbl-fairness-novig-mcheck.html"))
```
       
##Willingnes to accept

```{r 2045_post_accept}

res_main <-  lm(accept ~ treatment, data = d) 
res_main <- broom::tidy(res_main)

labels <- data.frame(
  term = c(
    "treatmentLamenting politician",
    "treatmentGeneral Prime",
    "treatmentSpecific prime",
    "treatmentWinner"
    
  ),
  label = c( "Lamenting politician",
             "General prime",
             "Specific prime",
             "Winner")
)
#Figure
fig <-   res_main %>%
  filter(term != "(Intercept)") %>% 
  left_join(labels, by = "term") %>% 
  
  ggplot(aes(x = estimate, y = label,
             xmin = estimate - (2 * std.error),
             xmax = estimate + (2 * std.error))) +
   geom_errorbarh(height = 0) +
  geom_point() +
  geom_vline(aes(xintercept = 0), linetype = "dotted") +
  scale_x_continuous(limits = c(-1, 1),
                     breaks = round(seq(-1, 1, .25), 2),
                     expand = c(0, 0)) +
  ggtitle('Treatment effects on willingness to accept outcome, Study 2 -- Norwegian vignette. Sample: Respondents who pass manipulation check') +
  labs(x = "Change in willingness to accept outcome",
       y = "Decision process attributes") +
  theme_bw() +
  theme(plot.margin = unit(c(2, 2, 2, 2), "mm"), axis.text.x=element_text(size=rel(0.7))) +
  theme(panel.spacing = unit(0.5, "lines"))
fig

ggsave(
  here("output", "novig", "figs", "pngs", "exp2-accept-mainfig-mcheck.png"),
  plot = fig,
  width = 5.5, height = 2.75
)

ggsave(
  here("output", "novig", "figs", "pdfs", "exp2-accept-mainfig-mcheck.pdf"),
  plot = fig,
  width = 5.5, height = 2.75
)


#Table
table <- res_main %>% 
  select(term, estimate, std.error, statistic, p.value) %>% 
  mutate(term = case_when( term == "(Intercept)" ~ "Not shown",
                    term == "treatmentLamenting politician" ~ "Lamenting politician",
                   term == "treatmentGeneral Prime" ~ "General prime", 
                   term == "treatmentSpecific prime" ~ "Specific prime",
                   term == "treatmentWinner" ~ "Winner"))

kable(table, booktabs = TRUE, caption = "Treatment effects on willingness to accept decision, Study 2 -- Norwegian vignette. Sample: Respondents who pass manipulation check.", col.names = linebreak(c("Treatment value", "Estimate", "Std. Error", "t-statistic", "p value")), digits = 2) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))  %>% 
  cat(., file = here("output", "novig", "tbls", "html",  "tbl-accept-novig-mcheck.html"))
```

##Trust in politician


```{r 2045_post_trust}

res_main <-  lm(trust ~ treatment, data = d) 
res_main <- broom::tidy(res_main)

labels <- data.frame(
  term = c(
    "treatmentLamenting politician",
    "treatmentGeneral Prime",
    "treatmentSpecific prime",
    "treatmentWinner"
    
  ),
  label = c( "Lamenting politician",
             "General prime",
             "Specific prime",
             "Winner")
)
#Figure
fig <-   res_main %>%
  filter(term != "(Intercept)") %>% 
  left_join(labels, by = "term") %>% 
  
  ggplot(aes(x = estimate, y = label,
             xmin = estimate - (2 * std.error),
             xmax = estimate + (2 * std.error))) +
   geom_errorbarh(height = 0) +
  geom_point() +
  geom_vline(aes(xintercept = 0), linetype = "dotted") +
  scale_x_continuous(limits = c(-1, 1),
                     breaks = round(seq(-1, 1, .25), 2),
                     expand = c(0, 0)) +
  labs(title = 'Treatment effects on trust in politicians, Study 2 -- Norwegian vignette.', 
       subtitle = 'Sample: Respondents who pass manipulation check',
       caption = '1 to 5 answer scale where 1 is lowest and 5 is highest') +
  theme_bw() +
  theme(plot.title = element_text(size= 9, face = 'bold'), plot.margin = unit(c(2, 2, 2, 2), "mm"), axis.text.x=element_text(size=rel(0.7))) +
  theme(panel.spacing = unit(0.5, "lines"))
fig

ggsave(
  here("output", "novig", "figs", "pngs", "exp2-trust-mainfig-mcheck.png"),
  plot = fig,
  width = 5.5, height = 2.75
)

ggsave(
  here("output", "novig", "figs", "pdfs", "exp2-trust-mainfig-mcheck.pdf"),
  plot = fig,
  width = 5.5, height = 2.75
)


#Table
table <- res_main %>% 
  select(term, estimate, std.error, statistic, p.value) %>% 
  mutate(term = case_when( term == "(Intercept)" ~ "Not shown",
                    term == "treatmentLamenting politician" ~ "Lamenting politician",
                   term == "treatmentGeneral Prime" ~ "General prime", 
                   term == "treatmentSpecific prime" ~ "Specific prime",
                   term == "treatmentWinner" ~ "Winner"))

kable(table, booktabs = TRUE, caption = "Treatment effects on trust in politician, Study 2 -- Norwegian vignette. Sample: Respondents who pass manipulation check.", col.names = linebreak(c("Treatment value", "Estimate", "Std. Error", "t-statistic", "p value")), digits = 2) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))  %>% 
  cat(., file = here("output", "novig", "tbls", "html",  "tbl-trust-novig-mcheck.html"))
```
