# Data management

>This chapter describes the data management that is conducted prior to any analysis

```{r 303_setup}
if(!require("codebook")){install.packages("codebook");  library(codebook)}
if(!require("dplyr")){install.packages("dplyr");  library(dplyr)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("naniar")){install.packages("naniar");  library(naniar)}
if(!require("openxlsx")){install.packages("openxlsx");  library(openxlsx)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}

d <- read_sav("Data/Goodloser-exp3-orig.sav")

knitr::opts_chunk$set(echo = TRUE, knitr.kable.NA = "", cache = FALSE, warning = FALSE)

```

##Exclude observations
> Exclude respondents who rush through the experiment. In line with the [pre-registration](GoogLoser_Prereg_3_#16823), these are defined as respondents who spend less than 25 percent of the median time on answering the questions are excluded from the analysis. 


```{r 303_exclude}
d <- d %>%
  mutate(median = median(time, na.rm = TRUE)) %>% 
  filter(time >= 0.25*median  )

d %>% 
  write_sav("Data/Goodloser-exp3.sav") %>%  #Create data file, .sav format
  write.csv("Data/Goodloser-exp3.csv")  #Create data file, .csv format
``` 



