# Pre-treatment, vignette, post-treatment

The statistics are displayed for the respondents of interest in this study, which is the respondents who end up with observing an unfavorable decision outcome in the experiment.
```{r 3031_setup, include=FALSE}
if(!require("broom")){install.packages("broom");  library(broom)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
options(kableExtra.latex.load_packages = FALSE) 
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("naniar")){install.packages("naniar");  library(naniar)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
# The analysis uses custom functions included in the compendium. Install the included pkg with `devtools::install()` or just install from github with:
#if (!require(wiggle)) {  devtools::install_github("mikajoh/wiggle")}

set.seed(2016)

d <- read_sav("Data/Goodloser-exp3-orig.sav")
e <- read_sav("Data/Goodloser-exp3-orig.sav")

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", warning = FALSE, message = FALSE)

```

```{r, include=F, eval=F }

e <- na_if(e, 97)
e <- na_if(e, 98)
e <-  e %>% mutate(treat_outfav = case_when(r13pad5_sak == 1 & r13pad1 == 1 & r13pad5_utfall == 1 ~ "Favorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 2 & r13pad5_utfall == 2 ~ "Favorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 1 & r13pad5_utfall == 2 ~ "Unfavorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 2 & r13pad5_utfall == 1 ~ "Unfavorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 1 & r13pad5_utfall == 1 ~ "Favorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 2 & r13pad5_utfall == 2 ~ "Favorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 1 & r13pad5_utfall == 2 ~ "Unfavorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 2 & r13pad5_utfall == 1 ~ "Unfavorable outcome")) %>% 
  filter(treat_outfav == "Unfavorable outcome")
```

```{r 3031_manage_data, include=F, eval=F}
d <- d %>% 
  mutate(
           treat_outfav = case_when(r13pad5_sak == 1 & r13pad1 == 1 & r13pad5_utfall == 1 ~ "Favorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 2 & r13pad5_utfall == 2 ~ "Favorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 1 & r13pad5_utfall == 2 ~ "Unfavorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 2 & r13pad5_utfall == 1 ~ "Unfavorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 1 & r13pad5_utfall == 1 ~ "Favorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 2 & r13pad5_utfall == 2 ~ "Favorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 1 & r13pad5_utfall == 2 ~ "Unfavorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 2 & r13pad5_utfall == 1 ~ "Unfavorable outcome"),
           r13pad1 = case_when(r13pad1 == 1 ~ "In favor",
                               r13pad1 == 2 ~ "Oppose"),
           r13pad2 = case_when(r13pad2 == 1 ~ "Not important at all",
                               r13pad2 == 2 ~ "Slightly important",
                               r13pad2 == 3 ~ "Somewhat important",
                               r13pad2 == 4 ~ "Important",
                               r13pad2 == 5 ~ "Very important"),
           r13pad2 = lvls_reorder(factor(r13pad2), c(2, 3, 4, 1, 5)),
           r13pad3 = case_when(r13pad3 == 1 ~ "In favor",
                               r13pad3 == 2 ~ "Oppose"),
           r13pad4 = case_when(r13pad4 == 1 ~ "Not important at all",
                               r13pad4 == 2 ~ "Slightly important",
                               r13pad4 == 3 ~ "Somewhat important",
                               r13pad4 == 4 ~ "Important",
                               r13pad4 == 5 ~ "Very important"),
           r13pad4 = lvls_reorder(factor(r13pad4), c(2, 3, 4, 1, 5)),
           r13pad6a = case_when(r13pad6a == 1 ~ "Not fair at all",
                                r13pad6a == 2 ~ "Slightly fair",
                                r13pad6a == 3 ~ "Somewhat fair",
                                r13pad6a == 4 ~ "Fair",
                                r13pad6a == 5 ~ "Very fair"),
           r13pad6a = lvls_reorder(factor(r13pad6a), c(2, 3, 4, 1, 5)),
           r13pad6b = case_when(r13pad6b == 1 ~ "1 Not fair",
                                r13pad6b == 2 ~ "2 ",
                                r13pad6b == 3 ~ "3",
                                r13pad6b == 4 ~ "4",
                                r13pad6b == 5 ~ "5 Most fair"),
           r13pad7a = case_when(r13pad7a == 1 ~ "Not reasonable at all",
                                r13pad7a == 2 ~ "Slightly reasonable",
                                r13pad7a == 3 ~ "Somewhat reasonable",
                                r13pad7a == 4 ~ "Reasonable",
                                r13pad7a == 5 ~ "Very reasonable"),
           r13pad7a = lvls_reorder(factor(r13pad7a), c(1, 3, 4, 2, 5)),
           r13pad7b = case_when(r13pad7b == 1 ~ "1 Not reasonable",
                                r13pad7b == 2 ~ "2 ",
                                r13pad7b == 3 ~ "3",
                                r13pad7b == 4 ~ "4",
                                r13pad7b == 5 ~ "5 Most reasonable"),
           r13pad8a = case_when(r13pad8a == 1 ~ "Not willing at all",
                                r13pad8a == 2 ~ "Slightly willing",
                                r13pad8a == 3 ~ "Somewhat willing",
                                r13pad8a == 4 ~ "Willing",
                                r13pad8a == 5 ~ "Very willing"),
           r13pad8a = lvls_reorder(factor(r13pad8a), c(1, 2, 3, 5, 4)),
           r13pad8b = case_when(r13pad8b == 1 ~ "1 Not willing",
                                r13pad8b == 2 ~ "2 ",
                                r13pad8b == 3 ~ "3",
                                r13pad8b == 4 ~ "4",
                                r13pad8b == 5 ~ "5 Most willing")
  )
```

```{r 3031_filter_losers}
d <- d %>%  mutate(
           treat_outfav = case_when(r13pad5_sak == 1 & r13pad1 == 1 & r13pad5_utfall == 1 ~ "Favorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 2 & r13pad5_utfall == 2 ~ "Favorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 1 & r13pad5_utfall == 2 ~ "Unfavorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 2 & r13pad5_utfall == 1 ~ "Unfavorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 1 & r13pad5_utfall == 1 ~ "Favorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 2 & r13pad5_utfall == 2 ~ "Favorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 1 & r13pad5_utfall == 2 ~ "Unfavorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 2 & r13pad5_utfall == 1 ~ "Unfavorable outcome")) %>% 
  filter(treat_outfav == "Unfavorable outcome")
```

## Pre-treatment measures
### Ban on begging - opinion
```{r 3031_pre1}
table <- d %>% mutate(r13pad1 = case_when(r13pad1 == 1 ~ "In favor",
                               r13pad1 == 2 ~ "Oppose")) %>% 
  group_by(r13pad1) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%
  ungroup()

#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on a ban on begging in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
  #save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on a ban on begging in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-begging-preference.html"))
```

### Ban on begging - importance
```{r 3031_pre2}
table <- d %>% 
     mutate(r13pad2 = case_when(r13pad2 == 1 ~ "Not important at all",
                               r13pad2 == 2 ~ "Slightly important",
                               r13pad2 == 3 ~ "Somewhat important",
                               r13pad2 == 4 ~ "Important",
                               r13pad2 == 5 ~ "Very important"),
           r13pad2 = lvls_reorder(factor(r13pad2), c(2, 3, 4, 1, 5))) %>% 
     group_by(r13pad2) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 

#For bookdown
kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of begging ban to you?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
#save to file
kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of begging ban to you?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-begging-importance.html"))
```
The mean score for the pre treatment measure "How important is the issue of begging ban to you?" is `r round(mean(e$r13pad2, na.rm=T), digits=2)`, and the standard deviation is `r round(sd(e$r13pad2, na.rm=T), digits=2)`.

### Toll on diesel cars - opinion
```{r 3031_pre3}
table <- d %>% mutate(r13pad3 = case_when(r13pad3 == 1 ~ "In favor",
                               r13pad3 == 2 ~ "Oppose")) %>% 
  group_by(r13pad3) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on an increase in the tolls for diesel cars in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
  #save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on an increase in the tolls for diesel cars in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-toll-preference.html"))
```

### Toll on diesel cars - importance
```{r 3031_pre4}
table <- d %>% mutate( r13pad4 = case_when(r13pad4 == 1 ~ "Not important at all",
                               r13pad4 == 2 ~ "Slightly important",
                               r13pad4 == 3 ~ "Somewhat important",
                               r13pad4 == 4 ~ "Important",
                               r13pad4 == 5 ~ "Very important"),
                        r13pad4 = lvls_reorder(factor(r13pad4), c(2, 3, 4, 1, 5))) %>% 
  group_by(r13pad4) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100))
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of increased tolls for diesel cars to you?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") 
  #save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of increased tolls for diesel cars to you?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-toll-preference.html"))
```
The mean score for the pre treatment measure "How important is the issue of increased tolls for diesel cars to you?" is `r round(mean(e$r13pad4, na.rm=T), digits=2)`, and the standard deviation is `r round(sd(e$r13pad4, na.rm=T), digits=2)`.

## Experimental vignette
```{r}
table <- tibble(Treatments = c("Issue", "Issue", "Outcome", "Outcome", "Winning margin", "Winning margin", "Winning margin", "Winner's gloating", "Winner's gloating", rep("Messenger and prime", 7)), 
                Value = c("Ban on begging", 
                          "Diesel car road toll",
                          "Yes",
                          "No",
                          "Not shown",
                          "Small margin",
                          "Large margin", 
                          "Not shown", 
                          "Yes", 
                          "Not shown", 
                          "Politician, no prime", 
                          "Politician,  specific good loser prime",
                          "Politician, generic good loser prime", 
                          "Newspaper, no prime",
                          "Newspaper, specific good loser prime", 
                          "Newspaper, generic good loser prime"), 
                Text = c("in the future, begging on the streets will be banned or permitted in the municipality. This is a controversial decision. Some residents are strong in favour of a ban (the “Yes” side), while other residents are strongly against a ban (the “No” side). Some",
                         "in the future, diesel cars will pay increased tolls. This is a controversial decision. Some residents are strongly in favour of such an increase (the side), while others are strongly against an increase (the “No” side). Some parties propose such an",
                         "The Yes side won the vote",
                         "The No side won the vote",
                         ".",
                         "with a slight majority.",
                         "with a large majority.",
                         " ",
                         "Following the decision, a politician on the winning side says that it was a good decision and that common sense prevailed.",
                         " ",
                         "The leader of one of the parties that was against the decision says that they are disappointed and that the decision was wrong.",
                         "The leader of one of the parties that was against the decision says that they are disappointed and that the decision was wrong,  but that it was a fair fight where both sides had the opportunity to argue in favour of their views.",
                         "The leader of one of the parties that was against the decision says that they are disappointed and that the decision was wrong,  but that is what living in a democracy is all about. Sometimes you win, sometimes you lose.",
                         "The local newspaper – which was against the decision – writes in an editorial that they are disappointed and that the decision was wrong.",
                         "The local newspaper – which was against the decision – writes in an editorial that they are disappointed and that the decision was wrong, but that it was a fair fight where both sides had the opportunity to argue in favour of their views.",
                         "The local newspaper – which was against the decision – writes in an editorial that they are disappointed and that the decision was wrong, but that is what living in a democracy is all about. Sometimes you win, sometimes you lose.")
)

#for bookdown
 table %>% 
    mutate_all(linebreak) %>% 
    kable(booktabs = T, linesep = "", escape = F,  caption = "Vignette treatment dimensions and values", col.names = linebreak(c("Preference", "Treatment", "Text"))) %>% 
    collapse_rows(columns = 1, latex_hline = "major", valign = "top") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position")) %>% 
   footnote(general = 'Experimental vignette (treatments in {curly brackets}): Below, we have described a hypothetical situation. Please read through the situation carefully and then answer the three questions that follow. Imagine that your municipality must decide on {Issue} The decision will be taken by the municipal council and follow the usual procedures. The proposal will initially be debated by the municipal council where all the members will have the opportunity to express their opinions and arguments regarding the issue. The debate will be public, and journalists will be in attendance to report on the debate. In the end, the politicians will vote on the issue. {Outcome} {[Winning margin} {Winner gloating} {Messenger and prime}') 
 
 #save to file
 table %>% 
    mutate_all(linebreak) %>% 
    kable(booktabs = T, linesep = "", escape = F,  caption = "Vignette treatment dimensions and values", col.names = linebreak(c("Preference", "Treatment", "Text"))) %>% 
    collapse_rows(columns = 1, latex_hline = "major", valign = "top") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position")) %>% 
   footnote(general = 'Experimental vignette (treatments in {curly brackets}): Below, we have described a hypothetical situation. Please read through the situation carefully and then answer the three questions that follow. Imagine that your municipality must decide on {Issue} The decision will be taken by the municipal council and follow the usual procedures. The proposal will initially be debated by the municipal council where all the members will have the opportunity to express their opinions and arguments regarding the issue. The debate will be public, and journalists will be in attendance to report on the debate. In the end, the politicians will vote on the issue. {Outcome} {[Winning margin} {Winner gloating} {Messenger and prime}') %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-vignette.html"))
```
## Post treatment measures
Please note that the the respondents were randomly assigned to either a worded answer scale, or a numbered answer scale. 
This accounts for the high share of NA's in the post treatment distribution tables.

### Evaluation
```{r 3031_post1}
table <- d %>%  mutate(r13pad6a = case_when(r13pad6a == 1 ~ "Not fair at all",
                                r13pad6a == 2 ~ "Slightly fair",
                                r13pad6a == 3 ~ "Somewhat fair",
                                r13pad6a == 4 ~ "Fair",
                                r13pad6a == 5 ~ "Very fair"),
           r13pad6a = lvls_reorder(factor(r13pad6a), c(2, 3, 4, 1, 5))) %>% 
  group_by(r13pad6a) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")  
#save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-eval-dv1.html"))

table <- d %>% mutate(r13pad6b = case_when(r13pad6b == 1 ~ "1 Not fair",
                                r13pad6b == 2 ~ "2 ",
                                r13pad6b == 3 ~ "3",
                                r13pad6b == 4 ~ "4",
                                r13pad6b == 5 ~ "5 Most fair")) %>% 
  group_by(r13pad6b) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100))
#for bookdown
 kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
 #save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-eval-dv2.html"))
```
The mean score for the pre treatment measure "What do you think about the way the decision was made?" is `r round(mean(e$r13pad6a, na.rm=T), digits=2)`, and the standard deviation is `r round(sd(e$r13pad6a, na.rm=T), digits=2)` for the worded answer scale.
For the numbered answer scale, the mean score is `r round(mean(e$r13pad6b, na.rm=T), digits=2)`, and the standard deviation is `r round(sd(e$r13pad6b, na.rm=T), digits=2)`

<!-- ### Reasonable decision -->
<!-- ```{r 3031_post2} -->
<!-- table <- d %>% mutate(r13pad7a = case_when(r13pad7a == 1 ~ "Not reasonable at all", -->
<!--                                 r13pad7a == 2 ~ "Slightly reasonable", -->
<!--                                 r13pad7a == 3 ~ "Somewhat reasonable", -->
<!--                                 r13pad7a == 4 ~ "Reasonable", -->
<!--                                 r13pad7a == 5 ~ "Very reasonable"), -->
<!--            r13pad7a = lvls_reorder(factor(r13pad7a), c(1, 3, 4, 2, 5))) %>%  -->
<!--   group_by(r13pad7a) %>% -->
<!--    summarize(N_obs = n()) %>%  -->
<!--   mutate(Percent_obs = round(N_obs/(sum(N_obs))*100))  -->
<!-- #for bookdown -->
<!--    kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How reasonable do you think the decision was?", col.names = linebreak(c("Value", "N", "Percent"))) %>%  -->
<!--   kable_styling(latex_options = "HOLD_position") -->
<!-- #save to file -->
<!--    kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How reasonable do you think the decision was?", col.names = linebreak(c("Value", "N", "Percent"))) %>%  -->
<!--   kable_styling(latex_options = "HOLD_position") %>%  -->
<!--   cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-reasonable-dv1.html")) -->

<!-- table <- d %>% mutate( r13pad7b = case_when(r13pad7b == 1 ~ "1 Not reasonable", -->
<!--                                 r13pad7b == 2 ~ "2 ", -->
<!--                                 r13pad7b == 3 ~ "3", -->
<!--                                 r13pad7b == 4 ~ "4", -->
<!--                                 r13pad7b == 5 ~ "5 Most reasonable")) %>%  -->
<!--   group_by(r13pad7b) %>% -->
<!--    summarize(N_obs = n()) %>%  -->
<!--   mutate(Percent_obs = round(N_obs/(sum(N_obs))*100))  -->
<!-- #for bookdown -->
<!--   kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How reasonable do you think the decision was?", col.names = linebreak(c("Value", "N", "Percent"))) %>%  -->
<!--   kable_styling(latex_options = "HOLD_position") -->

<!-- #save to file -->
<!--   kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How reasonable do you think the decision was?", col.names = linebreak(c("Value", "N", "Percent"))) %>%  -->
<!--   kable_styling(latex_options = "HOLD_position") %>%  -->
<!--   cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-reasonable-dv2.html")) -->
<!-- ``` -->
<!-- The mean score for the pre treatment measure "How reasonable do you think the decision was?" is `r round(mean(e$r13pad7a, na.rm=T), digits=2)`, and the standard deviation is `r round(sd(e$r13pad7a, na.rm=T), digits=2)` for the worded answer scale. -->
<!-- For the numbered answer scale, the mean score is `r round(mean(e$r13pad7b, na.rm=T), digits=2)`, and the standard deviation is `r round(sd(e$r13pad7b, na.rm=T), digits=2)` -->

### Acceptance
``` {r 3031_post3}
table <- d %>% mutate( r13pad8a = case_when(r13pad8a == 1 ~ "Not willing at all",
                                r13pad8a == 2 ~ "Slightly willing",
                                r13pad8a == 3 ~ "Somewhat willing",
                                r13pad8a == 4 ~ "Willing",
                                r13pad8a == 5 ~ "Very willing"),
           r13pad8a = lvls_reorder(factor(r13pad8a), c(1, 2, 3, 5, 4))) %>% 
  group_by(r13pad8a) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100))
#for bookdown
   kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "When you think about the actual outcome of the decision, how willing are you to accept the decision?", col.names = linebreak(c("Value", "N", "Percent"))) %>%   kable_styling(latex_options = "HOLD_position")
#save to file
   kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "When you think about the actual outcome of the decision, how willing are you to accept the decision?", col.names = linebreak(c("Value", "N", "Percent"))) %>%   kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-accept-dv1.html"))

table <- d %>% mutate(r13pad8b = case_when(r13pad8b == 1 ~ "1 Not willing",
                                r13pad8b == 2 ~ "2 ",
                                r13pad8b == 3 ~ "3",
                                r13pad8b == 4 ~ "4",
                                r13pad8b == 5 ~ "5 Most willing")) %>% 
  group_by(r13pad8b) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "When you think about the actual outcome of the decision, how willing are you to accept the decision?", col.names = linebreak(c("Value", "N", "Percent"))) %>%   kable_styling(latex_options = "HOLD_position")
#save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "When you think about the actual outcome of the decision, how willing are you to accept the decision?", col.names = linebreak(c("Value", "N", "Percent"))) %>%   kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-accept-dv2.html"))

```
The mean score for the pre treatment measure "When you think about the actual outcome of the decision, how willing are you to accept the decision?" is `r round(mean(e$r13pad8a, na.rm=T), digits=2)`, and the standard deviation is `r round(sd(e$r13pad8a, na.rm=T), digits=2)` for the worded answer scale.
For the numbered answer scale, the mean score is `r round(mean(e$r13pad8b, na.rm=T), digits=2)`, and the standard deviation is `r round(sd(e$r13pad8b, na.rm=T), digits=2)`
