# Pre-treatment, vignette, post-treatment
```{r 3031_setup, include=FALSE}
if(!require("broom")){install.packages("broom");  library(broom)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
options(kableExtra.latex.load_packages = FALSE) 
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("naniar")){install.packages("naniar");  library(naniar)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}
# The analysis uses custom functions included in the compendium. Install the included pkg with `devtools::install()` or just install from github with:
#if (!require(wiggle)) {  devtools::install_github("mikajoh/wiggle")}

set.seed(2016)

d <- read_sav("Data/Goodloser-exp3-orig.sav")

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", warning = FALSE, message = FALSE)
```
The experiment was fielded in Norway during the fall of 2018 through the 13th wave of [Norwegian Citizen Panel (NCP)](https://www.uib.no/medborger). The NCP  is a research-purpose internet panel with over 6000 active participants. It is based on a probability sample of the general Norwegian population above the age of 18 drawn from the Norwegian National Registry. The survey is based on a online questionnaire with postal recruitment. Panel members complete a questionnaire three times a year of 15 minutes each. The NCP is a core component of The Digital Social Science Core Facilities (DIGSSCORE), and  was established in 2013 as a collaboration between several departments at the Faculty of Social Sciences at the University of Bergen and NORCE -- Norwegian Research Centre. We refer to the [documentation report](Data/ncp-wave13-documentation.pdf) for further details on technical aspects of the survey, panel recruitment, response rates of the 13th wave, and representativeness. For details about the data collected in this project and the NCP at large, we refer to the [codebook for the Waves 1-13](Data/ncp-wave13-codebook.pdf).

## Pre-treatment measures
```{r}
d <- d %>% 
  mutate(
           r13pad1 = case_when(r13pad1 == 1 ~ "In favor",
                               r13pad1 == 2 ~ "Oppose"),
           r13pad2 = case_when(r13pad2 == 1 ~ "Not important at all",
                               r13pad2 == 2 ~ "Slightly important",
                               r13pad2 == 3 ~ "Somewhat important",
                               r13pad2 == 4 ~ "Important",
                               r13pad2 == 5 ~ "Very important"),
           r13pad2 = lvls_reorder(factor(r13pad2), c(2, 3, 4, 1, 5)),
           r13pad3 = case_when(r13pad3 == 1 ~ "In favor",
                               r13pad3 == 2 ~ "Oppose"),
           r13pad4 = case_when(r13pad4 == 1 ~ "Not important at all",
                               r13pad4 == 2 ~ "Slightly important",
                               r13pad4 == 3 ~ "Somewhat important",
                               r13pad4 == 4 ~ "Important",
                               r13pad4 == 5 ~ "Very important"),
           r13pad4 = lvls_reorder(factor(r13pad4), c(2, 3, 4, 1, 5)),
           r13pad6a = case_when(r13pad6a == 1 ~ "Not fair at all",
                                r13pad6a == 2 ~ "Slightly fair",
                                r13pad6a == 3 ~ "Somewhat fair",
                                r13pad6a == 4 ~ "Fair",
                                r13pad6a == 5 ~ "Very fair"),
           r13pad6a = lvls_reorder(factor(r13pad6a), c(2, 3, 4, 1, 5)),
           r13pad6b = case_when(r13pad6b == 1 ~ "1 Not fair",
                                r13pad6b == 2 ~ "2 ",
                                r13pad6b == 3 ~ "3",
                                r13pad6b == 4 ~ "4",
                                r13pad6b == 5 ~ "5 Most fair"),
           r13pad7a = case_when(r13pad7a == 1 ~ "Not reasonable at all",
                                r13pad7a == 2 ~ "Slightly reasonable",
                                r13pad7a == 3 ~ "Somewhat reasonable",
                                r13pad7a == 4 ~ "Reasonable",
                                r13pad7a == 5 ~ "Very reasonable"),
           r13pad7a = lvls_reorder(factor(r13pad7a), c(1, 3, 4, 2, 5)),
           r13pad7b = case_when(r13pad7b == 1 ~ "1 Not reasonable",
                                r13pad7b == 2 ~ "2 ",
                                r13pad7b == 3 ~ "3",
                                r13pad7b == 4 ~ "4",
                                r13pad7b == 5 ~ "5 Most reasonable"),
           r13pad8a = case_when(r13pad8a == 1 ~ "Not willing at all",
                                r13pad8a == 2 ~ "Slightly willing",
                                r13pad8a == 3 ~ "Somewhat willing",
                                r13pad8a == 4 ~ "Willing",
                                r13pad8a == 5 ~ "Very willing"),
           r13pad8a = lvls_reorder(factor(r13pad8a), c(1, 2, 3, 5, 4)),
           r13pad8b = case_when(r13pad8b == 1 ~ "1 Not willing",
                                r13pad8b == 2 ~ "2 ",
                                r13pad8b == 3 ~ "3",
                                r13pad8b == 4 ~ "4",
                                r13pad8b == 5 ~ "5 Most willing")
  )

table <- d %>% group_by(r13pad1) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) %>%
  ungroup()
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on a ban on begging in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
  #save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on a ban on begging in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-begging-preference.html"))

table <- d %>% group_by(r13pad2) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 

  #for bookdown
kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of begging ban to you?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
#save to file
kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of begging ban to you?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-begging-importance.html"))

table <- d %>% group_by(r13pad3) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on an increase in the tolls for diesel cars in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
  #save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What is your opinion on an increase in the tolls for diesel cars in your municipality?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-toll-preference.html"))

table <- d %>% group_by(r13pad4) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100))
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of increased tolls for diesel cars to you?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") 
  #save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How important is the issue of increased tolls for diesel cars to you?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-toll-preference.html"))
```

## Experimental vignette
```{r}
table <- tibble(Treatments = c("Issue", "Issue", "Outcome", "Outcome", "Winning margin", "Winning margin", "Winning margin", "Winner's gloating", "Winner's gloating", rep("Messenger and prime", 7)), 
                Value = c("Ban on begging", 
                          "Diesel car road toll",
                          "Yes",
                          "No",
                          "Not shown",
                          "Small margin",
                          "Large margin", 
                          "Not shown", 
                          "Yes", 
                          "Not shown", 
                          "Politician, no prime", 
                          "Politician,  specific good loser prime",
                          "Politician, generic good loser prime", 
                          "Newspaper, no prime",
                          "Newspaper, specific good loser prime", 
                          "Newspaper, generic good loser prime"), 
                Text = c("in the future, begging on the streets will be banned or permitted in the municipality. This is a controversial decision. Some residents are strong in favour of a ban (the “Yes” side), while other residents are strongly against a ban (the “No” side). Some",
                         "in the future, diesel cars will pay increased tolls. This is a controversial decision. Some residents are strongly in favour of such an increase (the side), while others are strongly against an increase (the “No” side). Some parties propose such an",
                         "The Yes side won the vote",
                         "The No side won the vote",
                         ".",
                         "with a slight majority.",
                         "with a large majority.",
                         " ",
                         "Following the decision, a politician on the winning side says that it was a good decision and that common sense prevailed.",
                         " ",
                         "The leader of one of the parties that was against the decision says that they are disappointed and that the decision was wrong.",
                         "The leader of one of the parties that was against the decision says that they are disappointed and that the decision was wrong,  but that it was a fair fight where both sides had the opportunity to argue in favour of their views.",
                         "The leader of one of the parties that was against the decision says that they are disappointed and that the decision was wrong,  but that is what living in a democracy is all about. Sometimes you win, sometimes you lose.",
                         "The local newspaper – which was against the decision – writes in an editorial that they are disappointed and that the decision was wrong.",
                         "The local newspaper – which was against the decision – writes in an editorial that they are disappointed and that the decision was wrong, but that it was a fair fight where both sides had the opportunity to argue in favour of their views.",
                         "The local newspaper – which was against the decision – writes in an editorial that they are disappointed and that the decision was wrong, but that is what living in a democracy is all about. Sometimes you win, sometimes you lose.")
)

#for bookdown
 table %>% 
    mutate_all(linebreak) %>% 
    kable(booktabs = T, linesep = "", escape = F,  caption = "Vignette treatment dimensions and values", col.names = linebreak(c("Preference", "Treatment", "Text"))) %>% 
    collapse_rows(columns = 1, latex_hline = "major", valign = "top") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position")) %>% 
   footnote(general = 'Experimental vignette (treatments in {curly brackets}): Below, we have described a hypothetical situation. Please read through the situation carefully and then answer the three questions that follow. Imagine that your municipality must decide on {Issue} The decision will be taken by the municipal council and follow the usual procedures. The proposal will initially be debated by the municipal council where all the members will have the opportunity to express their opinions and arguments regarding the issue. The debate will be public, and journalists will be in attendance to report on the debate. In the end, the politicians will vote on the issue. {Outcome} {[Winning margin} {Winner gloating} {Messenger and prime}') 
 
 #save to file
 table %>% 
    mutate_all(linebreak) %>% 
    kable(booktabs = T, linesep = "", escape = F,  caption = "Vignette treatment dimensions and values", col.names = linebreak(c("Preference", "Treatment", "Text"))) %>% 
    collapse_rows(columns = 1, latex_hline = "major", valign = "top") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position")) %>% 
   footnote(general = 'Experimental vignette (treatments in {curly brackets}): Below, we have described a hypothetical situation. Please read through the situation carefully and then answer the three questions that follow. Imagine that your municipality must decide on {Issue} The decision will be taken by the municipal council and follow the usual procedures. The proposal will initially be debated by the municipal council where all the members will have the opportunity to express their opinions and arguments regarding the issue. The debate will be public, and journalists will be in attendance to report on the debate. In the end, the politicians will vote on the issue. {Outcome} {[Winning margin} {Winner gloating} {Messenger and prime}') %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-vignette.html"))
```

```{r}

table <- d %>% group_by(r13pad6a) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")  
#save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-eval-dv1.html"))

table <- d %>% group_by(r13pad6b) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100))
#for bookdown
 kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
 #save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "What do you think about the way the decision was made?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-eval-dv2.html"))

table <- d %>% group_by(r13pad7a) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 
#for bookdown
   kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How reasonable do you think the decision was?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
#save to file
   kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How reasonable do you think the decision was?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-reasonable-dv1.html"))

table <- d %>% group_by(r13pad7b) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How reasonable do you think the decision was?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position")
  
#save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "How reasonable do you think the decision was?", col.names = linebreak(c("Value", "N", "Percent"))) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-reasonable-dv2.html"))


table <- d %>% group_by(r13pad8a) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100))
#for bookdown
   kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "When you think about the actual outcome of the decision, how willing are you to accept the decision?", col.names = linebreak(c("Value", "N", "Percent"))) %>%   kable_styling(latex_options = "HOLD_position")
#save to file
   kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "When you think about the actual outcome of the decision, how willing are you to accept the decision?", col.names = linebreak(c("Value", "N", "Percent"))) %>%   kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-accept-dv1.html"))

table <- d %>% group_by(r13pad8b) %>%
   summarize(N_obs = n()) %>% 
  mutate(Percent_obs = round(N_obs/(sum(N_obs))*100)) 
#for bookdown
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "When you think about the actual outcome of the decision, how willing are you to accept the decision?", col.names = linebreak(c("Value", "N", "Percent"))) %>%   kable_styling(latex_options = "HOLD_position")
#save to file
  kable(table, booktabs = TRUE, linesep = "", escape = F, caption = "When you think about the actual outcome of the decision, how willing are you to accept the decision?", col.names = linebreak(c("Value", "N", "Percent"))) %>%   kable_styling(latex_options = "HOLD_position") %>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-nocon-accept-dv2.html"))

```
