
# Effects on losers

>This chapter explores the second hypothesis in the [pre-registration](GoogLoser_Prereg_3_#16823[16065].pdf) of the experiment: ** Individuals that receive an unfavorable outcome and a procedural prime express higher fairness perceptions  than individuals that receive an unfavorable outcome and no procedural prime.** There is no support for this hypothesis in the analysis of the results.



```{r 305_setup, include=FALSE}
if(!require("broom")){install.packages("broom");  library(broom)}
if(!require("haven")){install.packages("haven");  library(haven)}
if(!require("here")){install.packages("here");  library(here)}
options(kableExtra.latex.load_packages = FALSE) 
if(!require("kableExtra")){install.packages("kableExtra");  library(kableExtra)}
if(!require("knitr")){install.packages("knitr");  library(knitr)}
if(!require("naniar")){install.packages("naniar");  library(naniar)}
if(!require("tidyverse")){install.packages("tidyverse");  library(tidyverse)}

set.seed(2016)

d <- read_sav("Data/Goodloser-exp3.sav")

knitr::opts_chunk$set(echo = FALSE, knitr.kable.NA = "", warning = FALSE, message = FALSE)
```

##Prepare data 
```{r 305_loser}

main_01 <- d %>% 
  mutate(rsp_id = as.numeric(responseid),
         rsp_beg = case_when(r13pad1 == 1 ~ "In favour of ban on begging",
                             r13pad1 == 2 ~ "Against ban on begging"),
         rsp_beg_imp = case_when(r13pad2 %in% 1:2 ~ "Important",
                                  r13pad2 %in% 3:5 ~ "Not important"),
         rsp_toll = case_when(r13pad3 == 1 ~ "In favour of road toll increase of diesel cars",
                              r13pad3 == 2 ~ "Against road toll increase of diesel cars"),
         rsp_toll_imp = case_when(r13pad4 %in% 1:2 ~ "Important",
                                  r13pad4 %in% 3:5 ~ "Not important"),
         treat_outcome = case_when(r13pad5_utfall == 1 ~ "The Yes side won the vote",
                                 r13pad5_utfall == 2 ~ "The No side won the vote"),
         treat_outfav = case_when(r13pad5_sak == 1 & r13pad1 == 1 & r13pad5_utfall == 1 ~ "Favorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 2 & r13pad5_utfall == 2 ~ "Favorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 1 & r13pad5_utfall == 2 ~ "Unfavorable outcome",
                                  r13pad5_sak == 1 & r13pad1 == 2 & r13pad5_utfall == 1 ~ "Unfavorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 1 & r13pad5_utfall == 1 ~ "Favorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 2 & r13pad5_utfall == 2 ~ "Favorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 1 & r13pad5_utfall == 2 ~ "Unfavorable outcome",
                                  r13pad5_sak == 2 & r13pad3 == 2 & r13pad5_utfall == 1 ~ "Unfavorable outcome"),
         treat_issue = case_when(r13pad5_sak == 1 ~ "Ban on begging",
                               r13pad5_sak == 2 ~ "Road toll increase of diesel cars"),
         treat_winningmargin = case_when(r13pad5_vinnermargin == 1 ~ "Not shown",
                                       r13pad5_vinnermargin == 2 ~ "Slight majority",
                                       r13pad5_vinnermargin == 3 ~ "Large majority"),
         treat_winnergloat = case_when(r13pad5_vinner == 1 ~ "Not shown",
                                     r13pad5_vinner == 2 ~ "Winning politician gloats"),
        treat_prime = case_when(r13pad5_avsender == 1 ~ "Not shown",
                               r13pad5_avsender == 2  | r13pad5_avsender == 5 ~ "No prime",
                               r13pad5_avsender == 3  | r13pad5_avsender == 6 ~ "Specific prime",
                               r13pad5_avsender == 4 | r13pad5_avsender == 7 ~ "General prime"),
         treat_messenger = case_when(r13pad5_avsender %in% 3:4 ~ "Political leader",
                                   r13pad5_avsender %in% 6:7 ~ "Local newspaper"),
         post_fair = case_when(r13pad6a == 1 | r13pad6b == 1 ~ 5,
                          r13pad6a == 2 | r13pad6b == 2 ~ 4,
                          r13pad6a == 3 | r13pad6b == 3 ~ 3,
                          r13pad6a == 4 | r13pad6b == 4 ~ 2,
                          r13pad6a == 5 | r13pad6b == 5 ~ 1),
          post_reasonable = case_when(r13pad7a == 1 | r13pad7b == 1 ~ 5,
                          r13pad7a == 2 | r13pad7b == 2 ~ 4,
                          r13pad7a == 3 | r13pad7b == 3 ~ 3,
                          r13pad7a == 4 | r13pad7b == 4 ~ 2,
                          r13pad7a == 5 | r13pad7b == 5 ~ 1),
          post_accept = case_when(r13pad8a == 1 | r13pad8b == 1 ~ 5,
                          r13pad8a == 2 | r13pad8b == 2 ~ 4,
                          r13pad8a == 3 | r13pad8b == 3 ~ 3,
                          r13pad8a == 4 | r13pad8b == 4 ~ 2,
                          r13pad8a == 5 | r13pad8b == 5 ~ 1)

  ) %>% 

  replace_with_na_all(condition = ~.x == 98 )%>%  #Recode 98 (not asked) as missing
  filter(!is.na(r13pad6_ran)) %>%  #Remove NA's
## We want the value labels in particular order for the tables and figures.
        mutate(treat_winningmargin = lvls_reorder(treat_winningmargin, c(2, 3, 1)), 
               treat_prime = lvls_reorder(treat_prime, c(3, 2, 4, 1)) 
        )
               
    main_01 <- main_01 %>%   
      filter(treat_outfav == "Unfavorable outcome")
``` 

###Number of losers 

The number of respondents with an unfavorable decision outcome is `r main_01 %>% summarise(n())` 


##Reasonable
```{r 305_post_reasonable_loser}

source("Functions/amce.R")

res_main <-  main_01 %>%
  amce(post_reasonable, treat_winningmargin, treat_winnergloat, treat_prime, treat_messenger) 
  
res_main <- res_main %>% 
  mutate(
  treatment =  case_when(treatment == "treat_outfav" ~ "Outcome\nfavor-\nability",
            treatment == "treat_winningmargin" ~ "Winning\nmargin",
            treatment == "treat_winnergloat" ~ "Winner\ngloats",
            treatment == "treat_prime" ~ "Democratic\nprime",
            treatment == "treat_messenger" ~ "Primer")
)

#Figure
fig_amce <-
  res_main %>%
  ggplot(aes(x = estimate, y = value)) +
  facet_grid(
    treatment ~ .,
    scales = "free_y",
    space = "free_y") +
  geom_errorbarh(
    aes(xmin = estimate - (2 * std_error),
        xmax = estimate + (2 * std_error)),
    height = 0) +
  geom_point() +
  geom_vline(aes(xintercept = 0), linetype = "dotted") +
  scale_x_continuous(
    limits = c(-1, 1),
    breaks = round(seq(-1, 1, .1), 2),
    expand = c(0, 0)) +
   labs(
    x = "Marginal effect, reasonable decision",
    y = "Decision process attributes") +
  theme_bw() +
  theme(plot.margin = unit(c(2, 2, 2, 2), "mm"),         axis.text.x=element_text(size=rel(0.7))) +
  theme(panel.spacing = unit(0.5, "lines"))
fig_amce

ggsave(
  here("output", "nocon", "figs", "pngs", "fig_losers_reasonable.png"),
  plot = fig_amce,
  width = 5.5, height = 2.75
)

ggsave(
  here("output", "nocon", "figs", "pdfs", "fig_losers_reasonable.pdf"),
  plot = fig_amce,
  width = 5.5, height = 2.75
)

#Table
res_main <- res_main %>% 
  select(value, estimate, std_error, statistic, p_value)

kable(res_main, booktabs = TRUE, caption = "Average Marginal Component Effects", col.names = linebreak(c("Treatment value", "Estimate", "Std. Error", "t-statistic", "p value")), digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>% 
 group_rows(index = c("Winning margin" = 3, "Winner gloating" = 2, "Good loser prime" = 4, "Primer" = 2))%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-losers-reasonable-nocon.html"))

```

##Willingnes to accept
```{r 305_post_accept_loser}


source("Functions/amce.R")

res_main <-  main_01 %>%
  amce(post_accept, treat_winningmargin, treat_winnergloat, treat_prime, treat_messenger) 
  
res_main <- res_main %>% 
  mutate(
  treatment =  case_when(treatment == "treat_outfav" ~ "Outcome\nfavor-\nability",
            treatment == "treat_winningmargin" ~ "Winning\nmargin",
            treatment == "treat_winnergloat" ~ "Winner\ngloats",
            treatment == "treat_prime" ~ "Democratic\nprime",
            treatment == "treat_messenger" ~ "Primer")
)

#Figure
fig_amce <-
  res_main %>%
  ggplot(aes(x = estimate, y = value)) +
  facet_grid(
    treatment ~ .,
    scales = "free_y",
    space = "free_y") +
  geom_errorbarh(
    aes(xmin = estimate - (2 * std_error),
        xmax = estimate + (2 * std_error)),
    height = 0) +
  geom_point() +
  geom_vline(aes(xintercept = 0), linetype = "dotted") +
  scale_x_continuous(
    limits = c(-1, 1),
    breaks = round(seq(-1, 1, .1), 2),
    expand = c(0, 0)) +
   labs(
    x = "Marginal effect, willingnes to accept decision",
    y = "Decision process attributes") +
  theme_bw() +
  theme(plot.margin = unit(c(2, 2, 2, 2), "mm"),         axis.text.x=element_text(size=rel(0.7)))
fig_amce

ggsave(
  here("output", "nocon", "figs", "pngs", "fig_losers_accept.png"),
  plot = fig_amce,
  width = 5.5, height = 4.75
)

ggsave(
  here("output", "nocon", "figs", "pdfs", "fig_losers_accept.pdf"),
  plot = fig_amce,
  width = 5.5, height = 4.75
)

#table
res_main <- res_main %>% 
  select(value, estimate, std_error, statistic, p_value)


kable(res_main, booktabs = TRUE, caption = "Average Marginal Component Effects", col.names = linebreak(c("Treatment value", "Estimate", "Std. Error", "t-statistic", "p value")), digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>% 
 group_rows(index = c("Winning margin" = 3, "Winner gloating" = 2, "Good loser prime" = 4, "Primer" = 2))%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-losers-accept-nocon.html"))

```

##Fairness perceptions

```{r 305_post_fair_loser}


source("Functions/amce.R")

res_main <-  main_01 %>%
  amce(post_fair, treat_winningmargin, treat_winnergloat, treat_prime, treat_messenger) 
  
res_main <- res_main %>% 
  mutate(
  treatment =  case_when(treatment == "treat_outfav" ~ "Outcome\nfavor-\nability",
            treatment == "treat_winningmargin" ~ "Winning\nmargin",
            treatment == "treat_winnergloat" ~ "Winner\ngloats",
            treatment == "treat_prime" ~ "Democratic\nprime",
            treatment == "treat_messenger" ~ "Primer")
)

#Figure
fig_amce <-
  res_main %>%
  ggplot(aes(x = estimate, y = value)) +
  facet_grid(
    treatment ~ .,
    scales = "free_y",
    space = "free_y") +
  geom_errorbarh(
    aes(xmin = estimate - (2 * std_error),
        xmax = estimate + (2 * std_error)),
    height = 0) +
  geom_point() +
  geom_vline(aes(xintercept = 0), linetype = "dotted") +
  scale_x_continuous(
    limits = c(-1, 1),
    breaks = round(seq(-1, 1, .1), 2),
    expand = c(0, 0)) +
   labs(
    x = "Marginal effect, perceived fairness of decision",
    y = "Decision process attributes") +
  theme_bw() +
  theme(plot.margin = unit(c(2, 2, 2, 2), "mm"),
        axis.text.x=element_text(size=rel(0.7)))
fig_amce

ggsave(
  here("output", "nocon", "figs", "pngs", "fig_losers_fair.png"),
  plot = fig_amce,
  width = 5.5, height = 4.75
)

ggsave(
 here("output", "nocon", "figs", "pdfs", "fig_losers_fair.pdf"),
  plot = fig_amce,
  width = 5.5, height = 4.75
)

#table
res_main <- res_main %>% 
  select(value, estimate, std_error, statistic, p_value)


kable(res_main, booktabs = TRUE, caption = "Average Marginal Component Effects", col.names = linebreak(c("Treatment value", "Estimate", "Std. Error", "t-statistic", "p value")), digits = 2) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>% 
 group_rows(index = c("Winning margin" = 3, "Winner gloating" = 2, "Good loser prime" = 4, "Primer" = 2))%>% 
  cat(., file = here("output", "nocon", "tbls", "html",  "tbl-losers-fairness-nocon.html"))

```

